---
author: "Mike X."
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is a codebook that documents all of the items in the current version of the NIMH KSADS applet for MindLogger."
---


```{r setup, echo=FALSE}

#Load and parse data dictionary
library(tidyverse)
library(RCurl)
library(linguisticsdown)
library(knitr)
library(formattable)
#library(kableExtra)
#library(webshot)
#webshot::install_phantomjs()

#where the data dictionary for the applet is hosted:
dataPath <- getURL("https://raw.githubusercontent.com/hotavocado/KSADS_ML_Applet/master/data_dic.csv")

dataDic <- read_csv(dataPath)

#dataDic <- read_csv('/Users/mike.xiao/Documents/GitHub/HBN_EMA_NIMH2/data_dic_new.csv')

imagePath = 'imagePath'



#split into activities

#preq <- filter(dataDic, `Form Name` == 'pre_questionnaire')

#morning <- filter(dataDic, `Form Name` == 'morning_set')

#day <- filter(dataDic, `Form Name` == 'day_set')

#night <- filter(dataDic, `Form Name` == 'evening_set')

#rm(dataDic)




#functions


#parse question

getQ <- function (dataset, question_name) {
  
  #grab question
  question <- unique(filter(dataset, !!sym("Variable / Field Name") == question_name)[['Field Label']])
  
  #if there are multiple versions of the question (morning/day)
  if (length(question) > 1) {
    
    #add quotes to the beginnign and end of each version of the question
    question <- map(question, function (x) paste0('"', x, '"'))
    
    cat('**Question**:\r\n\r\n')
    cat('+ _Morning Version_: ', question[[1]], '\n + _Day/Evening Version_: ', question[[2]], sep = '')
    
  }
  
  else {
    
    #add quotes to the beginning and end of each version of the question
    question <- paste0('"', question, '"')
    
    #add parsing for \r\n\r\n
    qlist <- as.list(str_split(question, '\\\\r\\\\n\\\\r\\\\n', simplify = T))
    
    if (length(qlist) > 1) {
    
      cat('**Question**:')
      
      for (i in 1:length(qlist)) {
        
        cat('\r\n\r\n', qlist[[i]], sep = '')
        
      } 
      
    }
    
    else {
      
      cat('**Question**: ', question, sep = '')
      
    }
    
  }
  
}

#parse header image

getHeadImg <- function (dataset, question_name) {
  
  filename <- unique(filter(dataset, !!sym("Variable / Field Name") == question_name)[['headerImage']])
    
  path <- paste0(imagePath, filename)
  
  if (is.na(filename)) {
  
    cat('**Header Image**: _None_')
  
  }
  
  else {
    
    cat('**Header Image**: ')
    include_graphics2(path)
  
  }
  
}


#parse visibility

getVis <- function (dataset, question_name) {
  
  visibility <- unique(filter(dataset, !!sym("Variable / Field Name") == question_name)[['Branching Logic (Show field only if...)']])
  
  if (is.na(visibility)) {
    return("**Visibility**: _Always_")
  }
  
  else {
    return(paste0("**Visibility**: ", visibility))
  }
  
}

#parse input type

getInputType <- function (dataset, question_name) {
  
  inputType <- unique(filter(dataset, !!sym("Variable / Field Name") == question_name)[['Field Type']])
  
  multipleChoice <- unique(filter(dataset, !!sym("Variable / Field Name") == question_name)[['multipleChoice']])
  
  allInputType <- c('markdown-message', 'radio', 'slider', 'time', 'timeRange', 'dropdown', 'date', 'notes', 'text', 'descriptive', 'checkbox')
  
  allInputText <- c('User Message/instructions', 'Single-select radio button', 'Slider bar', 'Time input', 'Time-range input', 'Dropdown select', 'Date picker', 'Text input', 'Text input', 'User Message/instructions', 'Multi-select checkbox')
  inputDic <- setNames(as.list(allInputText), allInputType)
  
  
  if (!is.na(multipleChoice)) {
    return('**Item Type**: Multi-select checkbox')
  }
  
  else {
    return(paste0('**Item Type**: ', inputDic[[inputType]]))
  }
  
}


#parse responses

#this function is used to process each choice in response object for image/no image
parseResponseChoice <- function (x) {

  if (length(x) == 2) {
    
    x[[3]] <- ''
    return(x)
    
  }

  else {
    
    x[[3]] <- paste0('<img src="', imagePath, x[[3]], '.png" width="60">')
    return(x)
  
  }

}

#this function creates the reponse object in the codebook based on input type
parseResponse <- function(dataset, question_name) {
  
  #get reponse info from csv
  choices <- unique(filter(dataset, !!sym("Variable / Field Name") == question_name)[["Choices, Calculations, OR Slider Labels"]])
  
  choiceType <- unique(filter(dataset, !!sym("Variable / Field Name") == question_name)[["Field Type"]])
  
 #temporary fix, revert later
  minVal <- unique(filter(dataset, !!sym("Variable / Field Name") == question_name)[["minVal"]])

  maxVal <- unique(filter(dataset, !!sym("Variable / Field Name") == question_name)[["maxVal"]])

  
  #for input types with empty choices
  if (choiceType %in% c('time', 'timeRange')) {
    
    return('**Responses**: _Time in HH:MM AM/PM format via clock widget_')
    
  }
  
  else if (choiceType == 'markdown-message') {
    
    return('**Responses**: _This item is a markdown message_')
    
  }
  
   else if (choiceType == 'date') {
    
    return('**Responses**: _Date via date picker widget_')
    
   }
  
  else if (choiceType == 'text') {
    
    return('**Responses**: _Free text entry_')
    
  }
  
  else if (choiceType == 'notes') {
    
    return('**Responses**: _Free text entry_')
    
  }
  
  else if (choiceType == 'descriptive') {
    
    return('**Responses**: _This item is a markdown message_')
    
  }
  
  else {
    
    choicesTable <- choices %>% 
    #parse the reponses 
    str_split(pattern = " \\| ") %>% 
    map(~str_split(., pattern = ", ")) %>% 
    flatten() %>%
    map(parseResponseChoice) %>%
    tibble(nested = .) %>%
    mutate(Value = map_chr(nested, ~.[[1]]),
           Label = map_chr(nested, ~.[[2]]),
           Image = map_chr(nested, ~.[[3]])
           ) %>% 
    select(-nested)
  #for slider, replace label of min and max responses with minVal and maxVal
    if (choiceType == 'slider') {

      choicesTable[['Label']][[1]] <- minVal
      choicesTable[['Label']][[nrow(choicesTable)]] <- maxVal
  
    }
    
    #for reponses where there isn't a single image, remove the image column
    if (length(unique(choicesTable$Image)) == 1) {
      
      choicesTable <- choicesTable[1:2]
      
    }

  return(choicesTable)
    
  }
  
} 



```

---
title: "`r paste0('Applet Codebook: NIMH KSADS ', dataDic$version[[1]])`"
---



# (PART) About {-}

# About this applet {#intro .unnumbered} 

This applet was made based on the NIMH KSADS on Redcap. These sections are in currently in progress:

+ Register Interview Child Psychiatric
+ Alcohol Abuse and Dependence
+ Drug Use
+ Caffeine
+ Interviewer Observation
+ GAF Scale
+ Interviewer Notes

The data dictionary used to generate this applet is [here](https://github.com/hotavocado/KSADS_ML_Applet/blob/master/data_dic.csv).


*These questions were constructed as part of a collaboration between the National Institute of Mental Health and the MATTER Lab of the Child Mind Institute (https://matter.childmind.org).*

<!--chapter:end:index.Rmd-->

# (PART) KSADS Sections {-}

# Timeline {#timeline_section}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'timeline')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`


<!--chapter:end:01-timeline.Rmd-->

# Screener {#screener_section}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'screener')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`

<!--chapter:end:02-screener.Rmd-->

# Screener Checklist {#screener_checklist}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'screener_checklist')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`

<!--chapter:end:03-screener_checklist.Rmd-->

# Major Depression {#context_section}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'major_depression')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`

<!--chapter:end:04-major_depression.Rmd-->

# Mania/Hypomania {#mania_section}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'maniahypomania')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`

<!--chapter:end:05-maniahypomania.Rmd-->

# Suicide/Self-Harm {#suicide_section}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'suicideselfharm')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`


<!--chapter:end:06-suicideselfharm.Rmd-->

# Psychosis {#activity_section}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'psychosis')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`

<!--chapter:end:07-pyschosis.Rmd-->

# Specific Phobia {#specific_phobia_section}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'specific_phobia')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`

<!--chapter:end:08-specific_phobia.Rmd-->

# Social Anxiety {#social_anxiety}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'social_anxiety')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`

<!--chapter:end:09-social_anxiety.Rmd-->

# Generalized Anxiety {#gad_section}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'overanxiousgad')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`

<!--chapter:end:10-overanxiousgad.Rmd-->

# Separation Anxiety {#separation_anxiety_section}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'separation_anxiety')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`

<!--chapter:end:11-separation_anxiety.Rmd-->

# Panic Disorder {#panic_section}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'panic_disorder')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`

<!--chapter:end:12-panic_disorder.Rmd-->

# Agoraphobia {#agoraphobia_section}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'agoraphobia')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`

<!--chapter:end:13-agoraphobia.Rmd-->

# Obsessive Compulsive Disorder {#ocd_section}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'obsessive_compulsive_disorder')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`

<!--chapter:end:14-obsessive_compulsive_disorder.Rmd-->

# Attention Deficit Hyperactivity Disorder  {#adhd_section}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'attention_deficit_hyperactivity_disorder')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`

<!--chapter:end:15-attention_deficit_hyperactivity_disorder.Rmd-->

# Oppositional Defiant Disorder {#odd_section}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'oppositional_defiant_disorder')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`

<!--chapter:end:16-oppositional_defiant_disorder.Rmd-->

# Conduct Disorder {#conduct_disorder_section}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'conduct_disorder')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`

<!--chapter:end:17-conduct_disorder.Rmd-->

# Eating Disorders {#eating_disorders_section}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'eating_disorders')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`

<!--chapter:end:18-eating_disorders.Rmd-->

# Post Traumatic Stress Disorder {#ptsd_section}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'posttraumatic_stress_disorder')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`

<!--chapter:end:19-posttraumatic_stress_disorder.Rmd-->

# Tobacco {#tobacco}

```{r, include=FALSE}

#get names of all questions from this section and generate codebook item objects for each

sectionQuestions <- unique(filter(dataDic, `Form Name` == 'tobacco')$`Variable / Field Name`)

sectionContent <- lapply(sectionQuestions, function(itemName) knit_expand(file = 'templates/itemTemplate.Rmd'))

```


`r knit(text = unlist(sectionContent))`

<!--chapter:end:20-tobacco.Rmd-->

